О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Rephrase a theorem to use a shorter notation

\begin{conjecture}
	\label{hyp:prime_planar}
	For every $m \geq 2$, $n \geq m+1$, $d \geq 1$ there exists an \textbf{prime}
	integral point set $M$ of $n$ points in $m$-dimensional Euclidean space
	where $M$ contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{conjecture}

>>>>

\begin{conjecture}
	\label{hyp:prime_planar}
	For every $m \geq 2$, $n \geq m+1$, $d \geq 1$ there exists an \textbf{prime}
	integral point set $M\in\mathfrak{M}(m,n)$ which
	contains points $M_1$ and $M_2$ such that distance between $M_1$ and $M_2$ is exactly $d$.
\end{conjecture}
